Woman and People with High Level of Education are More Concerend About Global Climate Change

### 2022-04-26 outputs/paper/paper.Rmd
change repo name

---
title: "Woman and People with High Level of Education are More Concerend About Global Climate Change"
author: 
  - Lantao Cui
thanks: "Code and data are available at: https://github.com/cuilantao/Toronto-s-reaction-to-fight-against-global-warming"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Climate change and global warming are predominant problems nowadays, in the north pole, polar ice caps are melting at a rate of almost 14% per decade. On top of that, over the past 30 years, the oldest and thickest ice in the north pole has declined by almost 95%. The majority of the Science Community believes that global warming is caused by the excessive emission of greenhouse gases such as Carbon Dioxide and Methane. Luckily, people are getting more and more aware of the global climate change and are willing to make changes. In this paper, we obtain a survey conducted on Toronto's residents about their perceptions of climate change and their willingness to take action on it. We aim to find out the impact of demographic factors such as personal income on people's perception of climate change. After careful investigation, we found out that woman and highly educated people are most concerned about climate change. Our findings can help the government to design better strategies to fight against global warming.\\par
 \\textbf{Keywords:} Climate Change, Demographic Factor, Gender, Income, Education, Age, Concern, Model"
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

>>>>

---
title: "Woman and People with High Level of Education are More Concerend About Global Climate Change"
author: 
  - Lantao Cui
thanks: "Code and data are available at: https://github.com/cuilantao/The-Impact-of-Demographic-Factors-on-People-s-Awareness-on-Climate-Change"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Climate change and global warming are predominant problems nowadays, in the north pole, polar ice caps are melting at a rate of almost 14% per decade. On top of that, over the past 30 years, the oldest and thickest ice in the north pole has declined by almost 95%. The majority of the Science Community believes that global warming is caused by the excessive emission of greenhouse gases such as Carbon Dioxide and Methane. Luckily, people are getting more and more aware of the global climate change and are willing to make changes. In this paper, we obtain a survey conducted on Toronto's residents about their perceptions of climate change and their willingness to take action on it. We aim to find out the impact of demographic factors such as personal income on people's perception of climate change. After careful investigation, we found out that woman and highly educated people are most concerned about climate change. Our findings can help the government to design better strategies to fight against global warming.\\par
 \\textbf{Keywords:} Climate Change, Demographic Factor, Gender, Income, Education, Age, Concern, Model"
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---
